BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-11-28 tex/5-evaluation.tex
Add first gnuplot figure.
Eval plan

\subsection{Introcution}
What is evaluated (not comments, iframes, authors, dates...)
\\ define the dataset and your competing algorithms the best way possible.

The dataset is a small sample coming from the Spinn3r dataset. The Spinn3r dataset was released for ICWSM 2011 conference.

\subsection{Content extraction}
Compare:
\begin{itemize}
  \item Our solution
  \item Boilerpipe https://github.com/misja/python-boilerpipe
  \item Goose https://github.com/grangier/python-goose
  \item Readability https://github.com/buriy/python-readability
\end{itemize}
On:
\begin{enumerate}
  \item Running time
  \begin{itemize}
    \item Plot duration as a function of the page length
    \item Plot duration as a function of the number or pages (our should only take time to build the rules)
  \end{itemize}
  \item Quality of output compared:
  \begin{itemize}
    \item Chart of success pourcentages
  \end{itemize}
\end{enumerate}

\subsection{JavaScript rendering}
Compare:
\begin{itemize}
  \item "Wget crawl" http://blogforever.eu/blog/2011/05/21/\\creating-a-snapshot-of-a-blog-post-using-wget/
  \item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/
  \item Selenium + full browser
  \item probably others
\end{itemize}
On:
\begin{itemize}
  \item Table comparing functionalities of each solution
  \item Histogram of redering time per browser\\(phantomjs/chrome/firefox)
\end{itemize}

- ez of use vs power, fine because it's automated
- c++ vs java vs scala vs go \cite{hundt2011}

>>>>

Our evaluation will be articulated in two parts. Firstly, we will compare the content extraction procedure presented in section \ref{algorithms} with three open source projects capable of generically extract content from web articles. The comparison will show that our blog targeted solution has better performances both in term of precision and running time. Secondly, a discussion will be held regarding the different alternative to archive data beyong HTML

% intro, plan
% hard to evaluate anything else, ttbook we r z only 1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}

% intro, plan

% other projects
\item Boilerpipe https://github.com/misja/python-boilerpipe
\item Goose https://github.com/grangier/python-goose
\item Readability https://github.com/buriy/python-readability
% limitation because different approach

% dataset
% result (table)
% discussion

% running time setup (single core, gc disabled, measure time spent in respective extraction functions)
% result (plot)
% discussion (c++ vs java vs scala vs go \cite{hundt2011})

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}

% intro, plan (why we pick these projects, what we want to show with this evaluation)

\item "Wget crawl" http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/
\item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/
\item OXPath
\item Selenium + full browser

% table to recap

% discussion (ez of use vs power, fine because it's automated)

\input{testfigure.tex}
